---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mapwtf

<!-- badges: start -->
<!-- badges: end -->

The goal of mapwtf is to plot topography for simple maps anywhere. Might become a 'automap()' like the 'SOmap_auto()' function in SOmap package. 

## Installation

You can install from github with 

``` r
remotes::install_github("mdsumner/mapwtf")
```

## Example

This is a basic example which shows you how to plot topography anywhere in any projection on the earth. Just replace 'reg' with your
projected raster to fill it with elevation values using `populate_topo()`. 


```{r example}
library(mapwtf)
for (i in seq_len(5)) {
  reg <- any_region(width = runif(1L, 50000, 5e6))
  x <- populate_topo(reg)
  raster::plot(x, col = hcl.colors(256))
  grat(x)
}



reg <- any_region(proj = "stere", width = 7e6, lat_0=-90, lon_0=147, lat_ts=-75)
x <- populate_topo(reg)
raster::plot(x, col = hcl.colors(256))
grat(x)

```


## Code of Conduct
  
Please note that the mapwtf project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
